---
title: "Final Exam IF-H"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Final Exam

## Instruction

1.  Read the instruction carefully and answer accordingly
2.  Do not cooperate with your friend
3.  The working time is 2 hours (01.00 - 03.00 PM) with additional 10 minutes to submit your work (03.10 PM)
4.  Submit the knitted pdf with name **Student ID_Name_Final Exam.pdf**

## Import Library (5 points)

Import all the required library.

```{r}
library(tidyverse)
library(tidymodels)
library(dplyr)
```

## Import Dataset (5 points)

Import zoo1.csv and zoo2.csv that are available on SPADA.

```{r}
zoo1 <- read_csv("dataset/zoo1.csv")
zoo2 <- read_csv("dataset/zoo2.csv")
```

## Preprocessing Data

### Join Table (10 points)

Join the datasets based on the same column.

```{r}
zoo <- inner_join(zoo1, zoo2, by = "animal_name")
```

### Data  Imputation (20 points)

The dataset contains N/A value in fins, legs, and tail columns. To fill the empty value, first, create a new dataset that is grouped by the class_type. Don't forget to create new columns to store the rounded mean of the fins, legs, and tail for each group.

```{r}
zoo_grouped_means <- zoo %>%
  group_by(class_type) %>%
  summarise(
    mean_fins = round(mean(fins, na.rm = TRUE)),
    mean_legs = round(mean(legs, na.rm = TRUE)),
    mean_tail = round(mean(tail, na.rm = TRUE))
  )
head(zoo_grouped_means, 5)
```

Then, left join the zoo dataset with the grouped dataset. After that, if the value of the column is N/A, the value will be filled with the mean value of the respective class_type, otherwise, the value remains the same.

```{r}
zoo <- zoo %>%
  left_join(zoo_grouped_means, by = "class_type") %>%
  mutate(
    fins = ifelse(is.na(fins), mean_fins, fins),
    legs = ifelse(is.na(legs), mean_legs, legs),
    tail = ifelse(is.na(tail), mean_tail, tail)
  )
head(zoo, 5)
```

### Choosing Columns (10 points)

Discard the mean columns.

```{r}
zoo <- zoo %>%
  select(-mean_fins, -mean_legs, -mean_tail)

head(zoo, 5)
```

## Data Visualization (12 points)

Create bar charts of legs for every class_type Because we have 16 class, there should be 6 charts. Use the function that we learned the other day, not manually. Feel free to use the help menu.

```{r}
zoo_type <- split(zoo, f = zoo$class_type)

plot_bar_chart <- function(data, class_label) {
  ggplot(data, aes(x = factor(legs))) +
    geom_bar() +
    labs(
      title = paste("Class Type:", class_label),
      x = "Animal Legs",
      y = "Count"
    ) +
    theme_minimal()
}

bar_charts <- lapply(names(zoo_type), function(class_label) {
  plot_bar_chart(zoo_type[[class_label]], class_label)
})

bar_charts[1:6]
```

## Data Modelling

### Data Splitting (5 points)

Split the zoo dataset for training and testing. Set the training ratio to 80% and split evenly based on the class_type. Show the summary of the training and testing data.

```{r}
set.seed(125)
split <- initial_split(zoo, prop = 0.8, strata = class_type)
training <- training(split)
testing <- testing(split)

cat("\nSummary Training \n")
summary(training)
cat("\nSummary Testing \n")
summary(testing)
```

### Creating Model (13 points)

Create a multinomial classification model.

```{r}
zoo_recipe <- recipe(class_type ~ ., data = training)

multinom_spec <- multinom_reg() %>%
  set_engine("nnet") %>%
  set_mode("classification")

zoo_workflow <- workflow() %>%
  add_recipe(zoo_recipe) %>%
  add_model(multinom_spec)

zoo_model <- zoo_workflow %>%
  fit(data = training)
```

## Evaluasi Model

### Testing Model (15 points)

Test the model using the testing data.

```{r}
zoo_predictions <- predict(zoo_model, testing, type = "class")

zoo_results <- testing %>%
  bind_cols(predictions = zoo_predictions)

head(zoo_results, 10)
```

### Confusion Matrix (5 points)

Create a confusion matrix for the test result.

```{r}
# zoo_conf_mat <- conf_mat(zoo_results)
# zoo_conf_mat <- conf_mat(zoo_results, truth = class_type, estimate = predictions$.pred_class)
# tidak bisa

```
