---
title: "Quiz IF-H"
author: "NIM_Quiz"
date: "2024-09-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instruction

1.  Answer by filling in the code chunk below each question.
2.  The allotted time for completion is 120 minutes (2 hours).
3.  NO CHEATING. 😠
4.  If there is any confusion about the questions, feel free to ask the assistant.
5.  Submit the file in .pdf format.
6.  Rename the author and the file to NIM_Kuis.

# Questions

0.  In this quiz, we will use a dataset called video_game_sales.\
    This dataset contains the top 100 best-selling video games from 1984 to 2015.\
    Run the code below to load the video_game_sales dataset. (2%)

    Dataset source: <https://www.kaggle.com/datasets/gregorut/videogamesales>

```{r}
# Nomor. 0
video_game_sales = data.frame(
  name = c(
    "Wii Sports",
    "Super Mario Bros.",
    "Mario Kart Wii",
    "Wii Sports Resort",
    "Pokemon Red/Pokemon Blue",
    "Tetris",
    "New Super Mario Bros.",
    "Wii Play",
    "New Super Mario Bros. Wii",
    "Duck Hunt",
    "Nintendogs",
    "Mario Kart DS",
    "Pokemon Gold/Pokemon Silver",
    "Wii Fit",
    "Wii Fit Plus",
    "Kinect Adventures!",
    "Grand Theft Auto V",
    "Grand Theft Auto: San Andreas",
    "Super Mario World",
    "Brain Age: Train Your Brain in Minutes a Day",
    "Pokemon Diamond/Pokemon Pearl",
    "Super Mario Land",
    "Super Mario Bros. 3",
    "Grand Theft Auto V",
    "Grand Theft Auto: Vice City",
    "Pokemon Ruby/Pokemon Sapphire",
    "Pokemon Black/Pokemon White",
    "Brain Age 2: More Training in Minutes a Day",
    "Gran Turismo 3: A-Spec",
    "Call of Duty: Modern Warfare 3",
    "Pokémon Yellow: Special Pikachu Edition",
    "Call of Duty: Black Ops",
    "Pokemon X/Pokemon Y",
    "Call of Duty: Black Ops 3",
    "Call of Duty: Black Ops II",
    "Call of Duty: Black Ops II",
    "Call of Duty: Modern Warfare 2",
    "Call of Duty: Modern Warfare 3",
    "Grand Theft Auto III",
    "Super Smash Bros. Brawl",
    "Call of Duty: Black Ops",
    "Animal Crossing: Wild World",
    "Mario Kart 7",
    "Halo 3",
    "Grand Theft Auto V",
    "Pokemon HeartGold/Pokemon SoulSilver",
    "Super Mario 64",
    "Gran Turismo 4",
    "Super Mario Galaxy",
    "Pokemon Omega Ruby/Pokemon Alpha Sapphire",
    "Super Mario Land 2: 6 Golden Coins",
    "Grand Theft Auto IV",
    "Gran Turismo",
    "Super Mario 3D Land",
    "Gran Turismo 5",
    "Call of Duty: Modern Warfare 2",
    "Grand Theft Auto IV",
    "Super Mario All-Stars",
    "Pokemon FireRed/Pokemon LeafGreen",
    "Super Mario 64",
    "Just Dance 3",
    "Call of Duty: Ghosts",
    "Halo: Reach",
    "Mario Kart 64",
    "New Super Mario Bros. 2",
    "Halo 4",
    "Final Fantasy VII",
    "Call of Duty: Ghosts",
    "Just Dance 2",
    "Gran Turismo 2",
    "Call of Duty 4: Modern Warfare",
    "Donkey Kong Country",
    "Minecraft",
    "Animal Crossing: New Leaf",
    "Mario Party DS"
  ),
  platform = as.factor(c(    
    "Wii", "NES", "Wii", "Wii", "GB", "GB",
    "DS", "Wii", "Wii", "NES", "DS", "DS",
    "GB", "Wii", "Wii", "X360", "PS3", "PS2",
    "SNES", "DS", "DS", "GB", "NES", "X360",
    "PS2", "GBA", "DS", "DS", "PS2", "X360",
    "GB", "X360", "3DS", "PS4", "PS3", "X360",
    "X360", "PS3", "PS2", "Wii", "PS3", "DS",
    "3DS", "X360", "PS4", "DS", "N64", "PS2",
    "Wii", "3DS", "GB", "X360", "PS", "3DS",
    "PS3", "PS3", "PS3", "SNES", "GBA", "DS",
    "Wii", "X360", "X360", "N64", "3DS", "X360",
    "PS", "PS3", "Wii", "PS", "X360", "SNES",
    "X360", "3DS", "DS"
  )),
  year = c(
    2006, 1985, 2008, 2009, 1996, 1989, 2006,
    2006, 2009, 1984, 2005, 2005, 1999, 2007,
    2009, 2010, 2013, 2004, 1990, 2005, 2006,
    1989, 1988, 2013, 2002, 2002, 2010, 2005,
    2001, 2011, 1998, 2010, 2013, 2015, 2012,
    2012, 2009, 2011, 2001, 2008, 2010, 2005,
    2011, 2007, 2014, 2009, 1996, 2004, 2007,
    2014, 1992, 2008, 1997, 2011, 2010, 2009,
    2008, 1993, 2004, 2004, 2011, 2013, 2010,
    1996, 2012, 2012, 1997, 2013, 2010, 1999,
    2007, 1994, 2013, 2012, 2007
  ),
  genre = as.factor(c(
    "Sports", "Platform", "Racing", "Sports", "RPG",
    "Puzzle", "Platform", "Misc", "Platform", "Shooter",
    "Simulation", "Racing", "RPG", "Sports", "Sports",
    "Misc", "Action", "Action", "Platform", "Misc", "RPG",
    "Platform", "Platform", "Action", "Action", "RPG", "RPG",
    "Puzzle", "Racing", "Shooter", "RPG", "Shooter",
    "RPG", "Shooter", "Shooter", "Shooter", "Shooter",
    "Shooter", "Action", "Fighting", "Shooter", "Simulation",
    "Racing", "Shooter", "Action", "Action", "Platform",
    "Racing", "Platform", "RPG", "Adventure", "Action",
    "Racing", "Platform", "Racing", "Shooter", "Action",
    "Platform", "RPG", "Platform", "Misc", "Shooter",
    "Shooter", "Racing", "Platform", "Shooter", "RPG",
    "Shooter", "Misc", "Racing", "Shooter", "Platform",
    "Misc", "Simulation", "Misc"
  )),
  us_sales = c(
    41.49, 29.08, 15.85, 15.75, 11.27, 23.2,
    11.38, 14.03, 14.59, 26.93, 9.07, 9.81, 9,
    8.94, 9.09, 14.97, 7.01, 9.43, 12.78, 4.75, 
    6.42, 10.83, 9.54, 9.63, 8.41, 6.06, 5.57,
    3.44, 6.85, 9.03, 5.89, 9.67, 5.17, 5.77,
    4.99, 8.25, 8.52, 5.54, 6.99, 6.75, 5.98,
    2.55, 4.74, 7.97, 3.8, 4.4, 6.91, 3.01,
    6.16, 4.23, 6.16, 6.76, 4.02, 4.89, 2.96,
    4.99, 4.76, 5.99, 4.34, 5.08, 6.05, 6.72,
    7.03, 5.55, 3.66, 6.63, 3.01, 4.09, 5.84,
    3.88, 5.91, 4.36, 5.58, 2.01, 4.46
  ),
  global_sales = c(
    82.74, 40.24, 35.82, 33, 31.37, 30.26, 30.01,
    29.02, 28.62, 28.31, 24.76, 23.42, 23.1, 22.72,
    22, 21.82, 21.4, 20.81, 20.61, 20.22, 18.36,
    18.14, 17.28, 16.38, 16.15, 15.85, 15.32, 15.3,
    14.98, 14.76, 14.64, 14.64, 14.35, 14.24, 14.03,
    13.73, 13.51, 13.46, 13.1, 13.04, 12.73, 12.27,
    12.21, 12.14, 11.98, 11.9, 11.89, 11.66, 11.52,
    11.33, 11.18, 11.02, 10.95, 10.79, 10.77, 10.69,
    10.57, 10.55, 10.49, 10.42, 10.26, 10.21, 9.88,
    9.87, 9.82, 9.76, 9.72, 9.59, 9.52, 9.49, 9.32,
    9.3, 9.2, 9.09, 9.02
  )
)

View(video_game_sales)
```

1.  Load dplyr library! (3%)

```{r}
library(dplyr)
```

2.  Show the top 5 best-selling games in the US for games released before 2000.\
    Show only the columns for the game name and total sales in the US. (10%)

```{r}
video_game_sales %>%
  filter(year < 2000) %>%
  arrange(desc(us_sales)) %>%
  select(name, us_sales) %>%
  head(5)
```

3.  Show all columns name on video_game_sales dataset! (5%)

```{r}
names(video_game_sales)
```

4.  Show the data type of the "genre" column.\
    At the bottom of the code, explain why the "genre" column uses this data type. (10%)

```{r}
class(video_game_sales$genre)
```

Explanation: Genre column has factor data type because it stores categorical data, with 11 different genres in the dataset.

5.  Show the top 5 games on the "X360" platform sorted by the most recent release year.\
    Show all columns except for the "us_sales" column. (11%)

```{r}
video_game_sales %>%
  filter(platform == "X360") %>%
  arrange(desc(year)) %>%
  select(-us_sales) %>%
  head(5)
```

6.  Create a classification in the dataframe based on "us_sales" with the following conditions:

    -   Sales above 10 are categorized as "Profit"
    -   Sales between 5-10 are categorized as "Moderate" (5 and 10 included)
    -   Sales below 5 are categorized as "Loss"

    Store the result in a new variable called 'sales_category'. (12%)

```{r}
sales_category = ifelse(video_game_sales$us_sales > 10, "Profit",
                         ifelse(video_game_sales$us_sales > 5, "Loss", "Moderate"))
sales_category
```

7.  Add the "sales_category" column as a new column to the dataframe.\
    Display the top 7 data entries sorted by global_sales. (12%)

```{r}
video_game_sales= mutate(video_game_sales, sales_category)

video_game_sales %>%
  arrange(desc(global_sales)) %>%
  head(7)
```

8.  Take 6 entries (rows) from each category in the 'sales_category' classification.\
    Combine these entries into a new dataframe named "new_video_game_sales".\
    After that, display the "new_video_game_sales" dataframe! (15%)

    (The resulting dataframe "new_video_game_sales" will contain 18 rows).

```{r}
# No. 8
```

9.  Display the average and total of global_sales grouped by genre! (12%)

```{r}
# No. 9
```

10. Create a barplot with the x-axis representing the name of the genre & the\
    y-axis representing the average sales from the results of question 9! (10%)

```{r}
# No. 10
```

11. Create a histogram with the following condition:

    -   x-axis representing the year of game release
    -   y-axis representing the number of games released in that year.

    Below the code chunk, write a conclusion that can be drawn from the histogram you created! (13%)

```{r}
# No. 11
```

Conclusion: ...

FIGHTING
